The regularity of ODEs and thimble integrals \\ with respect to Borel summation \begin{draft}\textbf{[DRAFT]}\end{draft}

### 2024-06-30 exp-resurgence.tex
Define dualsingexp colimit space

We will often make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough.
\begin{todo}\par
[Cite \cite{sternin1995borel} better for the theorem. Note that these results don't depend on which cotangent fiber we're mapping into. $\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.]
\end{todo}
%
\begin{prop}[following~\cite{sternin1995borel}]\label{prop:laplace-cont}
Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less. For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, with a norm of at most $\Gamma(\sigma)$.
\end{prop}
\begin{proof}
Given some $\phi \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta_\alpha, 0}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
\end{align*}
where $c_{z, \theta}$ is the cosine of $\arg(z) + \theta$. When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta|$ grows. This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta \phi$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$. It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta \phi$ match where their domains overlap. We can therefore glue these functions together into one big Laplace transform of $\phi$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.

@@

\begin{todo}[define $\widehat{\Omega}_\alpha^\bullet$]\end{todo} of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.

>>>>

We will often make statements about $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ that hold when $\Lambda$ is large enough. Since restriction gives an inclusion $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda) \hookrightarrow \dualsingexp{\sigma}(\widehat{\Omega}_\alpha^{\Lambda'})$ whenever $\Lambda < \Lambda'$, we can define a colimit space $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\bullet)$ that all of the spaces $\dualsingexp{\sigma}(\widehat{\Omega}_\alpha^\Lambda)$ include into. \begin{todo}\textbf{A} improve definition; \textbf{V} is this definition descriptive enough?\end{todo}
\begin{todo}\par
[Cite \cite{sternin1995borel} better for the theorem. Note that these results don't depend on which cotangent fiber we're mapping into. $\widehat{\Omega}$ is defined across all cotangent fibers over ordinary points.]
\end{todo}
%
\begin{prop}[following~\cite{sternin1995borel}]\label{prop:laplace-cont}
Let $\Omega_\alpha$ be an open sector with $\zeta = \alpha$ at its tip, and an opening angle of $\pi$ or less. For any $\sigma > 0$ and $\Lambda \ge 0$, and any angle $\theta$ in the opening of $\Omega_\alpha$, the Laplace transform $\laplace_{\zeta_\alpha, 0}^\theta$ is a continuous map $\singexp{\sigma-1}{\Lambda}(\Omega_\alpha) \to \dualsingexp{-\sigma}(\widehat{\Omega}_\alpha^\Lambda)$, with a norm of at most $\Gamma(\sigma)$.
\end{prop}
\begin{proof}
Given some $\phi \in \singexp{\sigma-1}{\Lambda}(\Omega_\alpha)$, we compute
\begin{align*}
|\laplace_{\zeta_\alpha, 0}^\theta \phi| & = \left| \int_{\mathcal{J}_{\zeta_\alpha, 0}^\theta} e^{-z\zeta_\alpha} \phi\,d\zeta_\alpha \right| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{-\Re(z\zeta_\alpha)} |\zeta_\alpha|^{\sigma-1} e^{\Lambda |\zeta_\alpha|} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha| \\
& \le \int_{\mathcal{J}_{\zeta_\alpha,0}^\theta} e^{(\Lambda - c_{z, \theta}|z|)|\zeta_\alpha|} |\zeta_\alpha|^{\sigma-1} \|\phi\|_{\sigma-1, \Lambda}\,|d\zeta_\alpha|,
\end{align*}
where $c_{z, \theta}$ is the cosine of $\arg(z) + \theta$. When $|z|$ is large and $c_{z, \theta}$ is positive, the integrand shrinks exponentially as $|\zeta|$ grows. This shows that for each angle $\theta$ in the opening of $\Omega_\alpha$, the integral defining $\laplace_{\zeta_\alpha, 0}^\theta \phi$ converges in some region of $\widehat{\Omega}_\alpha^\Lambda$. It also shows that for different angles $\theta$, the functions $\laplace_{\zeta_\alpha, 0}^\theta \phi$ match where their domains overlap. We can therefore glue these functions together into one big Laplace transform of $\phi$, defined at large values of $|z|$ across the whole opening angle of $\widehat{\Omega}_\alpha^\Lambda$.

@@

\begin{todo}[\textbf{A} define $\widehat{\Omega}_\alpha^\bullet$]\end{todo} of the space $e^{-\alpha z} \dualsingexp{-\tau_\alpha}(\widehat{\Omega}_\alpha^\bullet)$ from Section~\ref{sec:reg-decay}.
